Coherent Hyper-Raman Four Wave Mixing Spectroscopies

### 2024-06-11 paper.tex
oops

Most quantitative methods in an n$^{th}$ order CMDS experiment are used to extract $\chi^{(n)}$ values for comparing the relative strength of nonlinear processes in different media. \cite{Zhu87, RN351, RN345}
The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
To our knowledge, only 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(3)}$ values to extract transition moments. \cite{Moilanen2009, Grechko2012}
Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.
It is thus useful to investigate how a simple treatment of orientational averaging can extract $\beta_{ijk}$ from a $\chi^{(3)}_{IJKL}$ expression.

@@

In the discussion that follows, we assume that a vibrational mode in the ground state, $\ket{g,v}$, is correlated to the frequency of a vibronic $\ket{e,v}$.\cite{Carlson1990}
If the frequency of $\ket{g,v}$ is written as $\omega_{gv} + \xi$, where $\xi$ is some external strain (e.g. molecular collisions), then the frequency of $\ket{e,v}$ is $\omega_{ev} + c\xi$, where c is a shift coefficient.
Similarly, we take the frequency of $\ket{e,0}$ as $\omega_{e0} \rightarrow \omega_{e0} + \xi$.
The strains shift resonance denominators, e.g., for $\omega_{ij} \rightarrow \omega_{ij} + c\xi$, as
\begin{equation}
	\Delta_{ij}(\xi) = \omega_{ij} + c\xi -\omega_k - i\Gamma_{ij} \equiv \Delta_{ij}(0) + c\xi
\end{equation}
Without loss of generality, we assume c = 1 for correlated modes and c = -1 for anti-correlated modes.
To understand the impact of inhomogeneity on spectral output, we convolute an output density matrix element $\rho_{ab}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Penner1976, Desiderio1979, Dick83_1, Carlson1990line} 
\begin{equation}\label{contour}
	\rho_{ab} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ab}(\xi)
\end{equation} 
While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{RN307} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpreted closed-form solutions. \cite{Dick83_1, Carlson1990line}
For clarity, we evaluate the linenarrowing characteristics of pathway Ia (\autoref{fig:doubsive}) in detail in Appendix.
The results for all pathways in \autoref{fig:doubsive} are summarized in \autoref{T:correlated}.

>>>>

Most quantitative methods in an n$^{th}$ order CMDS experiment are used to extract $\chi^{(n)}$ values for comparing the relative strength of nonlinear processes in different media. \cite{Zhu87, RN351, RN345}
The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
To our knowledge, only 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(3)}$ values to extract transition moments. \cite{Moilanen2009, RN245}
Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.
It is thus useful to investigate how a simple treatment of orientational averaging can extract $\beta_{ijk}$ from a $\chi^{(3)}_{IJKL}$ expression.

@@

In the discussion that follows, we assume that a vibrational mode in the ground state, $\ket{g,v}$, is correlated to the frequency of a vibronic $\ket{e,v}$.\cite{Carlson1990}
If the frequency of $\ket{g,v}$ is written as $\omega_{gv} + \xi$, where $\xi$ is some external strain (e.g. molecular collisions), then the frequency of $\ket{e,v}$ is $\omega_{ev} + c\xi$, where c is a shift coefficient.
Similarly, we take the frequency of $\ket{e,0}$ as $\omega_{e0} \rightarrow \omega_{e0} + \xi$.
The strains shift resonance denominators, e.g., for $\omega_{ij} \rightarrow \omega_{ij} + c\xi$, as
\begin{equation}
	\Delta_{ij}(\xi) = \omega_{ij} + c\xi -\omega_k - i\Gamma_{ij} \equiv \Delta_{ij}(0) + c\xi
\end{equation}
Without loss of generality, we assume c = 1 for correlated modes and c = -1 for anti-correlated modes.
To understand the impact of inhomogeneity on spectral output, we convolute an output density matrix element $\rho_{ab}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Penner1976, Desiderio1979, Dick83_1, Carlson1990line} 
\begin{equation}\label{contour}
	\rho_{ab} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ab}(\xi)
\end{equation} 
While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{druet1979line, RN307} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpreted closed-form solutions. \cite{Dick83_1, Carlson1990line}
For clarity, we evaluate the linenarrowing characteristics of pathway Ia (\autoref{fig:doubsive}) in detail in Appendix.
The results for all pathways in \autoref{fig:doubsive} are summarized in \autoref{T:correlated}.
